Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2020-05-18 supplementary.tex
Edit supplementary procedure

In the original proposal of the Martingale Residuals \citep{Therneau1990}, Breslow's estimator \citep{Breslow1974} was the prefered approach for estimating the cumulative baseline hazard. Under the assumption that there is no ties among the failure times, the Breslow's estimator is defined as:
\begin{equation} 
\hat{H}_0(t) = \sum_{t_{i} \leq t}\frac{\delta(t_i)}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})}.
\end{equation}
Covariates of the fitted model are incorporated in the denominator of the summation.
Procedure~\ref{alg:br} provides an explicit description of this algorithm.
\begin{algorithm}
\SetAlgoLined
\For{each regularization parameter $\lambda$}{
 Fit the model using all observations' time and status \;
 Obtain linear predictor $\hat{\eta}$ from the fitted model\;
 Compute $\hat{H}_0(t) = \sum_{t_{i} \leq t}\frac{\delta(t_i)}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})}$\;
 \For{each fold $k = 1,2,...,K$}{
  Use the training set $T_k$ to obtain $\hat{\beta}^{-k}$\;
  	\For{each obervation $i$ in the $k$th fold}{
  	Compute the Cross-validated Martingale Residual: $\hat{M}^{cv}_{i}  = \delta_{i} - \hat{H}_{0}(t_{i})\exp(X_i\Tr\hat\beta^{-k})$\;
  	Compute the Deviance Residual: $ d_{i} = \text{sgn}(\hat{M}^{cv}_{i})\sqrt{-2(\hat{M}^{cv}_{i} + \delta_{i}\log(\delta_{i} - \hat{M}^{cv}_{i}))}$\;
  	}
 }
 Compute the sum of squares: $\sum_{i}\hat{d}_{i}^2$
 }
 \caption{\label{alg:br} Compute cross-validated deviance residuals based on the Breslow estimator}
\end{algorithm}

@@

\cite{Kalbfleisch2011} proposed a cumulative hazard estimator that incorporates covariates. Assuming only a single failure occurs at $t_i$, based on the fitted values of $\hat{\bbeta}$, we can first compute linear predictors $\hat{\eta}_i$ at each observed failure time. Based on $\hat{\eta}_i$, we can compute a discrete hazard component at each observed failure time):
\begin{equation}
1 - \hat{\alpha}_{i} = 1 - \left( 1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})} \right)^{\exp(-\hat{\eta}_{i})},
\end{equation}
and aggregate them together into the cumulative hazard function:
\begin{equation} 
\hat{H}_0(t) = \sum_{t_{i} \leq t}(1 - \hat{\alpha}_i),
\end{equation}
Procedure~\ref{alg:kp} provides an explicit description of this algorithm.
\begin{algorithm}
\SetAlgoLined
\For{each regularization parameter $\lambda$}{
 Fit the model using all observations' time and status \;
 Obtain linear predictor $\hat{\eta}$ from the fitted model\;
 Compute $\hat{H}_0(t) = \sum_{t_{i} \leq t} \left\{1 -  \left(1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})} \right) ^{\exp(-\hat{\eta}_{i})}\right\}$\;
 \For{each fold $k = 1,2,...,K$}{
  Use the training set $T_k$ to obtain $\hat{\beta}^{-k}$\;
  	\For{each obervation $i$ in the $k$th fold}{
  	Compute the Cross-validated Martingale Residual: $\hat{M}^{cv}_{i}  = \delta_{i} - \hat{H}_{0}(t_{i})\exp(X_i\Tr\hat\beta^{-k})$\;
  	Compute the Deviance Residual: $ d_{i} = \text{sgn}(\hat{M}^{cv}_{i})\sqrt{-2(\hat{M}^{cv}_{i} + \delta_{i}\log(\delta_{i} - \hat{M}^{cv}_{i}))}$\;
  	}
 }
 Compute the sum of squares: $\sum_{i}\hat{d}_{i}^2$
 }
 \caption{\label{alg:kp} Compute cross-validated deviance residuals based on the Kalbfleisch and Prentice estimator}
\end{algorithm}

>>>>

In the original proposal of the Martingale Residuals \citep{Therneau1990}, Breslow's estimator \citep{Breslow1974} was the prefered approach for estimating the cumulative baseline hazard. Under the assumption that there is no ties among the failure times, the Breslow's estimator is defined as:
\begin{equation} 
\hat{H}_0(t) = \sum_{t_{i} \leq t}\frac{\delta(t_i)}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})}.
\end{equation}
Covariates of the fitted model are incorporated in the denominator of the summation.
Procedure~\ref{alg:brkp} includes an explicit description of this algorithm.
\begin{algorithm}
\SetAlgoLined
\For{each regularization parameter $\lambda$}{
 Fit the model using all observations' time and status \;
 Obtain linear predictor $\hat{\eta}$ from the fitted model\;
 \uIf{Use the Breslow's estimator}{
 $\hat{H}_0(t) = \sum_{t_{i} \leq t}\frac{\delta(t_i)}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})}$;
 }\ElseIf{Use the Kalbfleisch and Prentice estimator}{
  $\hat{H}_0(t) = \sum_{t_{i} \leq t} \left\{1 -  \left(1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})} \right) ^{\exp(-\hat{\eta}_{i})}\right\}$\;
 }
 \For{each fold $k = 1,2,...,K$}{
  Use the training set $T_k$ to obtain $\hat{\beta}^{-k}$\;
  	\For{each obervation $i$ in the $k$th fold}{
  	Compute the Cross-validated Martingale Residual: $\hat{M}^{cv}_{i}  = \delta_{i} - \hat{H}_{0}(t_{i})\exp(X_i\Tr\hat\beta^{-k})$\;
  	Compute the Deviance Residual: $ d_{i} = \text{sgn}(\hat{M}^{cv}_{i})\sqrt{-2(\hat{M}^{cv}_{i} + \delta_{i}\log(\delta_{i} - \hat{M}^{cv}_{i}))}$\;
  	}
 }
 Compute the sum of squares: $\sum_{i}\hat{d}_{i}^2$
 }
 \caption{\label{alg:brkp} Compute cross-validated deviance residuals based on the Breslow estimator and the Kalbfleisch and Prentice estimator}
\end{algorithm}

@@

\cite{Kalbfleisch2011} proposed a cumulative hazard estimator that incorporates covariates. Assuming only a single failure occurs at $t_i$, based on the fitted values of $\hat{\bbeta}$, we can first compute linear predictors $\hat{\eta}_i$ at each observed failure time. Based on $\hat{\eta}_i$, we can compute a discrete hazard component at each observed failure time):
\begin{equation}
1 - \hat{\alpha}_{i} = 1 - \left( 1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}_{j})} \right)^{\exp(-\hat{\eta}_{i})},
\end{equation}
and aggregate them together into the cumulative hazard function:
\begin{equation} 
\hat{H}_0(t) = \sum_{t_{i} \leq t}(1 - \hat{\alpha}_i),
\end{equation}
Procedure~\ref{alg:brkp} includes an explicit description of this algorithm.
